\documentclass[10pt]{ms-cv}
\begin{document}


%\input{resume/contacts.tex}
%\input{resume/skills.tex}
%\input{resume/experience.tex}
%\vspace{\baselineskip}
%\input{resume/education.tex}


\name{Mykyta Sikriier}
\position{Senior Software Developer}
\mobile{+48 570 304 834} 
\email{sikrinick+cv@gmail.com}
\github{sikrinick}
\linkedin{sikrinick}

\makecvheader

\begin{cvskills}
    \cvskill
        {Programming languages}
        {Kotlin, Swift, Java, Dart, TypeScript, Python, C++}
    \cvskill
        {Frameworks} 
        {Android SDK, iOS SDK, Spring Boot, Gradle, Bazel, KotlinPoet}
    \cvskill
        {Infrastructure}
        {Firebase, GMS, GitHub CI/CD, Gitlab CI/CD, Docker}
    %\cvskill
    %    {Philosophies}
    %    {OOP, FRP (Reactive), TDD, Multiplatform, Backend-driven UI}
    \cvskill{Languages}{Ukrainian, English, Polish}
\end{cvskills}


\cvsection[$\approx$ 8 years]{Experience}
\cvexperience
  {GFT}
  {Senior Android Developer}
  {Warsaw, Poland}
  {Oct 2022 - Present}
  {
    Worked on a Mobile Banking applications for European region for a digital-first bank.
    \newline
    Was a main code owner of User Onboarding, Authentication, and Security processes.
    \newline
    Proposed and implemented an initialization framework, that allowed decrease of app launch time by 40\%.
  }
\cvexperience
  {Natek}
  {Senior Android Developer}
  {Warsaw, Poland}
  {Feb 2022 - Sep 2022}
  {
    Worked on a Mobile Workplace UEM application for Android.
    \newline
    Was responsible for refactoring from Java to Kotlin and for increase of code quality.
  }
\cvexperience
  {Allegro}
  {Mobile Software Developer}
  {Warsaw, Poland}
  {Oct 2019 - Aug 2021}
  {
    Worked on an internal Backend-driven UI solution, that required knowledge of both Android, iOS, and Spring Boot.
    \newline
    Proposed and implemented a screenshot utility, that had positive impact on product quality.
    \newline
    Suggested and developed a code generation tool, that allowed usage of more than 700 template models as Kotlin code.
  }
\cvexperience
  {Vestiacom}
  {Android Developer}
  {Warsaw, Poland}
  {Aug 2018 - Sep 2019}
  {
    Initiated Reactive Programming approach, RxJava 2, in a project and provided documentation for adoption.
    \newline
    Proposed a way-of-working for refactoring existing 7-year-old codebase from Java to Kotlin.
  }
\cvexperience
  {Proexe}
  {Android Developer}
  {Warsaw, Poland}
  {Apr 2017 - Jul 2018}
  {
    Developed Android application for MedTech, which had integrated Bluetooth LE and C++ library via JNI.
    \newline
    Developed Application for USB Video Class (UVC) devices with real-time video stream over network and recording.
  }
\cvexperience
  {Freelancer}
  {Junior Software Developer}
  {Odesa, Ukraine}
  {Aug 2015 - Jul 2016}
  {
    Implemented an email tracking solution for an Android email client both in app and on backend.
  }

\vspace{\baselineskip}

\cvsection{Education}
\cvexperience
  {University of Warsaw}
  {M.A. in Quantitative Finance}
  {Warsaw, Poland}
  {Jan 2022}
  {Mathematics in Finance, Statistics, Financial Markets, Time Series Analysis, C++ and Python}

  %\cvexperience
%  {Odesa National Economic University}
%  {B.S. in Finance and Credit}
%  {Odesa, Ukraine}
%  {Sep 2011 - Jun 2015}
%  {Corporate Finance, Investment Theory, Money Theory, Accounting, Statistics and Mathematics}
%\cvexperience
%  {Odesa National University}
%  {B.S. in Law}
%  {Odesa, Ukraine}
%  {Sep 2011 - May 2016}
%  {Civil Law, Corporate Law, Tax Law, Finance Law}

\end{document}
