% !TeX root = ../cv.tex

\cvsection[$\approx$ 7 years]{Experience}
\cvexperience
  {GFT}
  {Senior Android Developer}
  {Warsaw, Poland}
  {Oct 2022 - Present}
  {
    Worked on Mobile Banking for SEA region,
    White-Label solution for Digital Banking, 
    \newline
    Mobile Banking application for European region.
  }
  {
    Worked on Mobile Banking for SEA region,
    White-Label solution for Digital Banking, 
    \newline
    Mobile Banking application for European region.
  }
\cvexperience
  {Natek}
  {Senior Android Developer}
  {Warsaw, Poland}
  {Feb 2022 - Sep 2022}
  {
    Mobile Workplace UEM application by VMWare for Android.
  }
  {
    Worked as a part of a VMWare team over a UEM application, mobile workplace. 
    \newline
    Was responsible for general support of application codebase, refactoring from Java to Kotlin and
    increasing code coverage levels and re-implementing risky parts of code.
    Implemented various new features as well.
  }
\cvexperience
  {Allegro}
  {Mobile Software Developer}
  {Warsaw, Poland}
  {Oct 2019 - Aug 2021}
  {
    Backend-driven UI solution. Android, Backend and Developer Tools. Rarely iOS.
    \newline
    Utilities for quality assurance. Code generation tools.
  }
  {
    Team was working on a framework, which allowed to create and serve app screens from backend without browsers.
    \newline
    Screen layouts were served on request from backend and a resulting screen had only native Android and iOS views.
    \newline
    As a part of a team, I was developing Core framework part.
    This required developing for Android and Backend, which was based on Spring Boot.
    Additionally, this position required development of Gradle plugins, screenshot testing utilities and
    other coding solutions for internal clients.
  }
\cvexperience
  {Vestiacom}
  {Android Developer}
  {Warsaw, Poland}
  {Aug 2018 - Sep 2019}
  {
    Smart Home application, support and refactoring from Java to Kotlin.
    \newline
    Android application for SMB protocol.
  }
  {
    Smart-home application for control over various devices via specialized WiFi-hotspot.
    Implementing support for new features and smart-home devices in Android application.
    Additionally, invoked and succeeded in refactoring code base from Java to Kotlin.
    \newline
    Proposed and started a practice of using reactive programming framework, RxJava 2, in that project.
    Occasional work with Redis due to project specifics.
  }
\cvexperience
  {Proexe}
  {Android Developer}
  {Warsaw, Poland}
  {Apr 2017 - Jul 2018}
  {
    MedTech app with BLE, chat and integration with third-party C++ libraries via JNI.
    \newline
    Application for USB Video Class (UVC) devices with real-time video stream over network and recording.
  }
  {
    Developed Android application for MedTech, which had integrated Bluetooth LE and C++ library via JNI.
    \newline
    Developed an Android application to control an inspection tool.
    An inspection tool is a camera on a telescopic tube with joystick and lights.
    Android application had to control camera settings, lights, allow simple image post-processing.
    Also, it served as a local video streaming server.
  }
\cvexperience
  {Freelancer}
  {Software Developer}
  {Odesa, Ukraine}
  {Aug 2015 - Jul 2016}
  {
    Mostly Android apps and support of CMS solutions.
  }
  {
    Developed and supported various minor Android apps. Among those were an email client and task management application.
    \newline
    Periodically, developed and supported Backend, mainly Node.js and Spring.
  }

